\Title

### 2015-11-03 manuscript.tex
Finished software implementation part

The implementation relies on the open-source libraries
scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
and seaborn
\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks (e.g., forward modeling).

@@

The Python implementation of the inversion as well as the Jupyter notebooks are
freely available under the terms of the BSD 3-clause open-source license.
Both can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
An archived version is also available at
\url{http://dx.doi.org/DOI_HERE} (made available upon publication).
\todo{Insert Zenodo DOI here}

\todo{Check which conjugate gradient scipy uses}

@@

%\begin{figure*}
    %\centering
    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
    %\caption{This is a figure caption.}
    %\label{fig:sam-data}
%\end{figure*}

%\begin{figure*}
    %\centering
    %\includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
    %\caption{This is a figure caption.}
    %\label{fig:sam-sed}
%\end{figure*}

>>>>

The inversion method proposed here is implemented in the Python programming
language.
The software is freely available
under the terms of the BSD 3-clause open-source software license.
Our implementation relies on the open-source libraries
scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
and seaborn
\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks,
particularly for forward modeling using tesseroids.
We use the scipy.sparse package for sparse matrix arithmetic and linear
algebra.

@@

All source code, data, and Jupyter notebooks
used here can be found at the online repository
\url{https://github.com/pinga-lab/paper-moho-inversion-tesseroids}.
An archived version is also available at
\url{http://dx.doi.org/DOI} (made available upon publication).
The repository also contains instructions for installing the necessary software
and reproducing all results presented here.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-data}
    \caption{This is a figure caption.}
    \label{fig:sam-data}
\end{figure*}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/paper/sam-gravity-sed}
    \caption{This is a figure caption.}
    \label{fig:sam-sed}
\end{figure*}
